%% Cover letter for IEEE Access submission
%% Compile with pdflatex
\documentclass[11pt, a4paper]{letter}
\usepackage{geometry}
\geometry{top=2.5cm, bottom=2.5cm, left=3cm, right=3cm}
\usepackage{url}
\usepackage{microtype}
\usepackage{parskip}

\signature{Florin Olariu\\
  Faculty of Computer Science\\
  Alexandru Ioan Cuza University of Ia\c{s}i, Romania\\
  \texttt{folariu@suvoda.com}\\[4pt]
  \small(on behalf of both authors)}

\address{Florin Olariu\\
  Faculty of Computer Science\\
  Alexandru Ioan Cuza University of Ia\c{s}i\\
  Bd.\ Carol I, Nr.\ 11, 700506 Ia\c{s}i\\
  Romania}

\date{\today}

\begin{document}

\begin{letter}{%
  Editor-in-Chief\\
  \textit{IEEE Access}
}

\opening{Dear Editor,}

We submit for consideration in \textit{IEEE Access} our manuscript,

\begin{center}
  \textbf{``A Skill-Mediated LLM Workflow for Migrating a .NET Monolith
  to Microservices: A Controlled Case Study''}
\end{center}

\textbf{What the paper reports.}
We present a controlled case study of a skill-mediated LLM workflow
applied end-to-end to a single .NET~10 monolith.  The workflow
composes ten Claude~Code skill scripts into a complete sequence:
requirements extraction, architecture analysis, microservices
decomposition, code generation, unit and integration testing,
automated review, automated security checks, automated remediation,
and gated publish.  The case study uses four publicly-available
artefacts: the monolith (Slice~1), a manually-engineered microservices
reference (Slice~2), the workflow's automated decomposition
(Slice~1~Refactored), and a Terraform configuration for Oracle Cloud
Infrastructure (Slice~3).

\textbf{What we measure.}
The paper reports empirical results from four measurement campaigns
on the primary case:
(i) structural alignment between the workflow's decomposition and the
independently-engineered manual reference, scored mechanically against
a pre-registered twenty-dimension rubric over ten repeated runs;
(ii) wall-clock duration of the automated decomposition compared to
the developer-time spent producing the manual reference;
(iii) a three-way ablation that separates skill-abstraction effect
from prompt-specificity effect, comparing the skill-mediated workflow
($N{=}10$) against both a fully-specified raw-LLM baseline ($N{=}10$)
and a matched-specificity minimal-prompt baseline ($N{=}5$); and
(iv) precision and recall of the workflow's automated security
checks on a 20-file matched-pair injection corpus covering ten common
.NET vulnerability classes.

\textbf{Headline result.}
The original 13.4-percentage-point skill-vs-baseline gap decomposes
into a 10.3-point prompt-specificity effect ($p < 0.001$) and a
3.2-point skill-abstraction effect that does not reach significance
at $\alpha{=}0.05$ ($p \approx 0.11$, $N{=}9$ vs.\ $N{=}4$). We did
not detect a difference between the skill abstraction and a
vague-prompt baseline on single-shot alignment quality. What the
skills do is remove the prompt-engineering burden: the
matched-specificity baseline requires a 100-word prompt to reach
74\% alignment, whereas the skill abstraction is invoked by typing
\texttt{/refactor}. The two short-prompt conditions exhibited one
failure each, of qualitatively different kinds (skill-invocation
vs.\ premature-exit); we report the failure modes as qualitative
findings rather than as a ranked reliability claim because the
Wilson 95\% intervals overlap on this sample. The wrapper's value
is ergonomics and the qualitative form of its failures, not better
LLM output.

\textbf{Transfer check on a second codebase.}
To establish that the headline finding is not specific to the
primary case, we re-ran the skill-mediated and baseline conditions
on Microsoft's \textit{eShopOnWeb} monolith --- a substantially
larger codebase in a different domain (.NET~8 e-commerce) ---
scored against Microsoft's active \textit{dotnet/eShop}
microservices reference, which is maintained independently of
this work.  The skill-vs-baseline gap replicates to within
0.1 percentage points across the two cases: $-13.4$~pp on the
primary case and $-13.3$~pp on the transfer case.

\textbf{Reproducibility.}
The skill scripts, both case-study codebases tagged at the
experimental commit, the raw run logs and transcripts, the scoring
scripts, the verifier changelog, the security injection corpus, and
a full environment manifest (LLM model identity, CLI version,
hardware, dependency versions) are deposited at Zenodo
(\texttt{10.5281/zenodo.20422420}) and cited by DOI in the
manuscript.  The exact configuration can be reproduced
under the same model identity; transfer to other monoliths,
languages, or models requires re-evaluation, and we discuss the
limits of the case-study scope explicitly in the threats-to-validity
section.

\textbf{Scope and limits.}
We present the workflow as a reproducible pilot, not as a validated
general-purpose migration tool.  We make no claim that the decomposition
quality, productivity figures, or security-check performance generalise
beyond the case study without additional evaluation.  The contribution
is the composition pattern plus the reproducibility deposit, evaluated
honestly on one concrete .NET codebase.

\textbf{Fit for \textit{IEEE Access}.}
\textit{IEEE Access} accommodates reproducible case studies that
combine engineering practice with empirical evaluation, which is the
shape of this work.  The manuscript is structured around a clear
methodology section, multi-run empirical measurements with mean and
standard deviation, a baseline isolation experiment, an ablation
of failure modes, and a precision-recall security evaluation.

\textbf{Authors and contributions.}
\begin{itemize}
  \item \textbf{Florin Olariu} (Alexandru Ioan Cuza University of
    Ia\c{s}i and Suvoda LLC) --- skill design and implementation,
    experimental harness, evaluation, writing.
  \item \textbf{Lenu\c{t}a Alboaie} (Alexandru Ioan Cuza University of
    Ia\c{s}i) --- manual microservices reference (Slice~2) produced
    independently of the skill prompts, scoring rubric design,
    independent verification pass, writing.
\end{itemize}

\textbf{Originality and ethics.}
This work has not been published elsewhere and is not under review
at any other venue.  No human or animal subjects are involved.  We
declare no conflicts of interest.

We thank you for your consideration and look forward to the
reviewers' assessment.

\closing{Respectfully yours,}

\end{letter}
\end{document}
