%% Cover letter for IEEE Software submission
%% Compile with pdflatex
\documentclass[11pt, a4paper]{letter}
\usepackage{geometry}
\geometry{top=2.5cm, bottom=2.5cm, left=3cm, right=3cm}
\usepackage{url}
\usepackage{microtype}
\usepackage{parskip}

\signature{Florin Olariu\\
  Faculty of Computer Science\\
  Alexandru Ioan Cuza University of Ia\c{s}i, Romania\\
  \texttt{folariu@suvoda.com}\\[4pt]
  \small(on behalf of both authors)}

\address{Florin Olariu\\
  Faculty of Computer Science\\
  Alexandru Ioan Cuza University of Ia\c{s}i\\
  Bd.\ Carol I, Nr.\ 11, 700506 Ia\c{s}i\\
  Romania}

\date{\today}

\begin{document}

\begin{letter}{%
  Prof.\ Sigrid Eldh\\
  Editor-in-Chief, \textit{IEEE Software}\\
  \texttt{sigrid.eldh@ieee.org}
}

\opening{Dear Prof.\ Eldh,}

We are pleased to submit our manuscript,

\begin{center}
  \textbf{``From Monolith to Cloud: An Agentic AI Pipeline
  for .NET Microservices Migration''}
\end{center}

for consideration in \textit{IEEE Software}.

\textbf{What the paper is about.}
We report a complete, end-to-end migration of \textit{PetRescue}, a
.NET~10 ASP.NET~Core monolith, to independently deployable
microservices running on Oracle Cloud Infrastructure---executed and
validated using a ten-skill agentic AI pipeline built on Claude~Code.

The research is structured around four public artefacts: Slice~1 (the
original monolith), Slice~2 (a hand-crafted microservices decomposition
produced independently by the second author as an expert reference),
Slice~1~Refactored (the AI-generated decomposition produced by the
pipeline), and Slice~3 (a Terraform configuration that deploys either
codebase to an OCI Ampere~A1.Flex ARM64 instance at zero cost on the
Always~Free tier).

The pipeline is grounded in three design principles---\emph{skill
atomicity}, \emph{artefact-mediated state}, and \emph{gated
autonomy}---that make it auditable, safe for CI/CD contexts, and
portable across projects.
The AI-generated decomposition matches the expert reference across all
twenty pre-defined structural dimensions---and was produced in
approximately \textbf{5~minutes}, compared to the \textbf{one
developer-day} the second author spent on the hand-crafted reference.
A new feature is added identically to both codebases in a complete
quality-gated cycle of approximately \textbf{30~minutes}, including
automated detection and remediation of seven critical and high-severity
security findings before the commit is permitted.
The pipeline terminates with a Terraform-managed cloud deployment.

\textbf{Why this matters to \textit{IEEE Software} readers.}
\textit{IEEE Software} bridges research and practice.  The productivity
numbers above are the kind of evidence practitioners need to evaluate
whether AI-assisted migration is worth adopting.  All four artefacts
are open-source at \url{https://github.com/florinolariuip}, so any
reader can reproduce or extend the results on their own codebase using
the same ten skill scripts---no modifications required.  We present
this explicitly as a \emph{reproducible pilot}: the skills are the
contribution; PetRescue is the validation vehicle.

\textbf{Three actionable insights} (as required by \textit{IEEE
Software}):
\begin{enumerate}
  \item The \texttt{/refactor} skill reproduces an expert architect's
        decomposition in approximately \textbf{5~minutes} vs.\
        \textbf{one developer-day} for manual migration, while
        independently inferring security patterns the skill prompt
        does not enumerate---demonstrating that LLMs carry substantial
        implicit architectural knowledge that structured prompting can
        reliably elicit.
  \item A complete quality-gated feature addition---code, review,
        security audit, automated fix, and gated commit---completes in
        approximately \textbf{30~minutes}, making the quality-assured
        path the fast path rather than an additional burden.
  \item Ten open-source Claude~Code skill scripts form a reproducible
        pilot any team can clone and run on their own .NET monolith:
        the methodology is the artefact, and it is fully open.
\end{enumerate}

\textbf{Word count.}  The manuscript is within the 4{,}200-word limit,
inclusive of three figures and two tables at 250~words each.  The
reference list contains 15~entries, at the stated limit.  Author
biographies are appended and not counted.

\textbf{Originality.}  This work has not been submitted elsewhere and
is not under review at any other venue.

\textbf{Authors and roles.}
\begin{itemize}
  \item \textbf{Florin Olariu} (Alexandru Ioan Cuza University of
    Ia\c{s}i \& Suvoda LLC) --- pipeline design and implementation,
    evaluation, writing.
  \item \textbf{Lenuta Alboaie} (Alexandru Ioan Cuza University of
    Ia\c{s}i) --- expert decomposition design (Slice~2 ground truth),
    evaluation methodology, writing.
\end{itemize}

We have no conflicts of interest to declare.  We welcome double-blind
review and will prepare an anonymised version upon request.

Thank you for considering our submission.  We look forward to your
editorial assessment.

\closing{Respectfully yours,}

\end{letter}
\end{document}
